A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-12 paper.tex

\begin{definition}
Let $m$ be a positive integer. Suppose $X$ is a complex manifold equipped with an $m$-th root $K_X^{1/m}$ of the canonical bundle, $Y, M, \fg$ are as before and $\fg$ is equipped with a weight grading $\fg=\oplus_n \fg(n)$ for which the symmetric pairing $\langle -, -\rangle$ on $\fg$ has weight $m$. We may consider a version of the generalized Chern--Simons theory with the bundle of BV fields
\[E = \bigoplus_n \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg(m)\otimes K_X^{n/m} [1]\]
and the symplectic pairing $\omega$ and the action functional as before where we do not use the holomorphic volume form on $X$.
\end{definition}

@@

\begin{example}
Consider the setting of Example \ref{ex:CSHamiltonianreduction}. The dg Lie algebra $\cL$ carries a weight grading, where we consider $\fg$ in weight 0, $V$ in weight $1$ and $\fg^*$ in weight $2$. With respec to this weight grading the bilinear pairing on $\fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
\[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, (U\otimes K_X^{1/2})\ham \fg).\]
\end{example}

@@

In this case $S_+\otimes W$ and $S_-\otimes W$ have two-dimensional trivial $G$-subrepresentations. Any scalar rank $(1, 1)$ supercharge is square-zero. We choose a homomorphism $\alpha\colon \U(1)\rightarrow G_R$ under which the first two summands in \eqref{eq:4d411decomposition} have weight $1$ and the last two summands have weight $-1$. This makes the chosen rank $(1, 1)$ supercharge have weight $1$.

@@

\subsubsection{Minimal Twist}
\label{sect:3dminimaltwist}
A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  
We use thetwisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$.

@@

>>>>

\begin{definition}
Let $m$ be a positive integer. Suppose $X$ is a complex manifold equipped with an $m$-th root $K_X^{1/m}$ of the canonical bundle, $Y, M, \fg$ are as before and $\fg$ is equipped with a weight grading $\fg=\oplus_n \fg(n)$ for which the symmetric pairing $\langle -, -\rangle$ on $\fg$ has weight $m$. We may consider a version of the generalized Chern--Simons theory with the bundle of BV fields
\[E = \bigoplus_n \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg(n)\otimes K_X^{n/m} [1]\]
and the symplectic pairing $\omega$ and the action functional as before where we do not use the holomorphic volume form on $X$.
\end{definition}

@@

\begin{example}
Consider the setting of Example \ref{ex:CSHamiltonianreduction}. The dg Lie algebra $\cL$ carries a weight grading, where we consider $\fg$ in weight 0, $V$ in weight $1$ and $\fg^*$ in weight $2$. With respect to this weight grading the bilinear pairing on $\fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
\[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, (U\otimes K_X^{1/2})\ham \fg).\]
\end{example}

@@

In this case $S_+\otimes W$ and $S_-\otimes W^*$ have two-dimensional trivial $G$-subrepresentations. Any scalar rank $(1, 1)$ supercharge is square-zero. We choose a homomorphism $\alpha\colon \U(1)\rightarrow G_R$ under which the first two summands in \eqref{eq:4d411decomposition} have weight $1$ and the last two summands have weight $-1$. This makes the chosen rank $(1, 1)$ supercharge have weight $1$.

@@

\subsubsection{Minimal Twist}
\label{sect:3dminimaltwist}
A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  
We use the twisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$.

@@

\begin{remark}
\brian{Cotangent type.}
\end{remark}
